%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Mulberry}{HTML}{72243D}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Sepia}
\colorlet{accent}{Mulberry}
\colorlet{emphasis}{Black}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{Mateus Macedo}
\tagline{Desenvolvedor Back-end}

\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \linkedin{linkedin.com/in/MateusMaceedo }
  \email{mateusouza2014@live.com }
  % \mailaddress{Ward No-13, Old Post Office Road,Khajuwala }
  \location{Rua Padre Gonçalo Leite - 05570-050 - SP }
  \phone{Tel..(11) 9 6424 9895 }
  \phone{Rec..(11) 9 6525-4135 }
  \divider
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}
  \github{github.com/MateusMaceedo }
%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[page1sidebar]{Experiência}

\cvevent{Everis Brasil}{Analista de Engenharia -- Setor Bancário Financiamento de Veículos}{8 mêses em 2021}{}
	\textbf{Cliente Itáu Unibanco} Participando e impulsionando mudanças e inovação no maior banco da américa latina. Automatizando tarefas de sistemas COBOL fortemente acoplados dentro de um mainframe e traduzi-los em soluções JAVA de microsserviço modernas. Seguindo as melhores práticas como TDD, BDD, DDD, Arquitetura Hexagonal, Domain Driven Design e sistemas de mensagens assíncronas com RabitMQ e KAFKA.
	
    \divider

	\cvtag{ \textbf{Cliente Itaú Unibanco - Financiamento de Veiculos}} 

    \divider

	\begin{itemize}
	\item Times e metodologia ágil.
	\item Testes automatizados; planejamento e execução de testes para aplicações mobile e website.
	\item Testes Funcionais, Integração, Performance, Mutação e Vulnerabilidade.
	\item Ferramentas de gestão de tarefas (ex: JIRA) ferramentas de planejamento de testes (ex: TM4J).
	\item Ferramentas de automação de testes (ex:Robot, jMeter, Selenium, Appium).
	\item Linguagens de programação usadas atualmente, Java/Kotlin/Dotnet.
	\item Frameworks de automação (Selenium, Appium, Cucumber, etc).
	\item Microserviços e documentação de API.
	\item Automação Web, API e Mobile.
	\item Execução em SilkTest e SilkCentral.
\end{itemize}

\
\

\cvevent{}{Backend -- Setor Bancário Consórcio de Veículos}{Atual em 2021}{}
\divider
\cvtag{ \textbf{Cliente Itaú Unibanco - Consórcio de Veiculos}} 
\divider
 Atuando na sustentação e modernização dos canais de contratação digitais, realizando implementações e manuntenções de incidentes, modernizando o backend da aplicação, tendo como base as seguintes atividades.
\divider
\begin{itemize}
\item Analise e ajustes de incidentes nos canais de contratação digital (Bankline e Mobile): Realizando automação de Robôs, analise e desenvolvimento de api, modernização da plataforma "Backend", automatizando processos para melhor performance da aplicação etc.
\item Melhorando a experiência de contratação digital dos clientes correntista e não correntista.
\item Testes de Usabilidade, Acessibilidade e Performance.

\cvevent{}{Frontend -- Freelance Setor Marketing}{jan. de 2020 - 8 meses}{}

\divider
\cvtag{ \textbf{Plataforma de divulgação de cursos EAD}} 
\item Experiência com atividades de desenvolvimento Mobile.
\item Capacidade comprovada de desenvolver linguagem Android (Kotlin e Java).
\item Trabalhei em projetos com metodologias ágeis.
\item Experiência com os serviços da plataforma Google Firebase.
\item Conhecimento de boas práticas de desenvolvimento e arquitetura de software (código limpo, TDD, BDD, CI / CD).
\item Prática com DevSecOps (integração contínua com Gradle, Maven, Jenkins, GitLab, Sonar, FortFy, ArtiFactory).
\item Experiência em metodologias de teste e qualidade de software.
\item Pipiline e Esteira de Produção (Jenkins).
\divider
\end{itemize}
\medskip
\clearpage
\end{document}
\profilepic{path/picture}
